Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-26 prop_letter.tex
Updates from ShareLaTeX

In conventional quantum theory, when we measure a property $\mathbf{O}$
of a physical system whose state is represented by a density matrix~$\rho$,
the probability to obtain the value $\lambda$ is determined by the
Born rule $\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{\lambda}\right)=\Tr\left(\rho P_{\lambda}\right)$,
where $P_{\lambda}$ denotes the projector onto the eigenspace corresponding
to the eigenvalue $\lambda$ of the Hermitian operator $\mathbf{O}$~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.

In other words, any density matrix~$\rho$ defines a function $\mu_{\rho}^{\mathrm{\mathrm{B}}}$
from the set of all projectors~$\events$ to $[0,1]$. This function~$\mu_{\rho}^{\mathrm{\mathrm{B}}}$
is called a quantum probability measure because it satisfies the following
probability axioms~\citep{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}: 
\begin{itemize}
\item $\mu_{\rho}^{\mathrm{\mathrm{B}}}(\mathbb{0})=0$. 
\item $\mu_{\rho}^{\mathrm{\mathrm{B}}}(\mathbb{1})=1$. 
\item For any projection $P$, $\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\mathbb{1}-P\right)=1-\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P\right)$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have 
\begin{equation}
\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumProbability-Addition}
\end{equation}
\end{itemize}
Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
satisfying the above axioms, Gleason's theorem asserts that there
exists a unique mixed state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$
in a Hilbert space of dimension $d\geq3$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.

>>>>

In conventional quantum theory, when we measure a property $\mathbf{O}$
of a physical system whose state is represented by a density matrix~$\rho$,
the probability to obtain the value $\lambda$ of that property is determined by the
Born rule $\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{\lambda}\right)=\Tr\left(\rho P_{\lambda}\right)$,
where $P_{\lambda}$ denotes the projector onto the eigenspace corresponding
to the eigenvalue $\lambda$ of the Hermitian operator
$\mathbf{O}$~\citep{Born1983,peres1995quantum,544199,Jaeger2007}. 
Alternatively, one may say that the state $\rho$ determines the 
probability measure $\mu_{\rho}^{\mathrm{\mathrm{B}}}$ defined as a
function from the set $\events$ of all possible projectors to the interval 
$[0,1]$, and satisfies the following probability axioms~
\citep{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}: 
\begin{itemize}
\item $\mu_{\rho}^{\mathrm{\mathrm{B}}}(\mathbb{0})=0$. 
\item $\mu_{\rho}^{\mathrm{\mathrm{B}}}(\mathbb{1})=1$. 
\item For any projection $P$, $\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\mathbb{1}-P\right)=1-\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P\right)$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have 
\begin{equation}
\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumProbability-Addition}
\end{equation}
\end{itemize}
Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
satisfying the above axioms, Gleason's theorem asserts that there
exists a unique mixed state~$\rho$ such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$
in a Hilbert space of dimension $d\geq3$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
